
\iffalse
(this is comments) change log:

TODO list:

 - evaluation
     - other app
 
 - related work:
    - vm migration related works

v5.8
 - grammar checking ongoing
 
v5.7, apr 23:

 - finalized for submission

 - new ordered introductions by shanhe
 
 - evaluation
     - figure descriptions
     
 - clean unused, reorg. latex files/folders
 
    
v5.6, apr23:
    
 - abstract
 
 - evaluation
     - update table optimized.
     
 - reorganize latex files/folders

v5.5, apr 23:

    - design and implementation:
        - system overview
        - predump, 
        - memdiff, 
        - compression, 
        - pipelined/paralled.

v5.4, apr 22:
    - new organization by Shanhe
    - add table frame to evaluation
    - new labels in ch3
    
v5.3, apr 22:

 - related work:
    - more citations, 29
    - openvz, lxc migration, comparison
    - edge computing related works
    - sataya vm handoff, vm synthesis. 
    


v5.2, apr 21:

 - new floating figure of sys implementation.
    - system arch figure
    - refer to sataya vm post-copy paper
    
 - done size data collection in auto-data scripts.

v5.1, apr 21:

 - new template from acm
    https://www.acm.org/publications/proceedings-template
 
v4.2, Apr 20: 

 - re-organize the sections/chapters
 
 - draw figure of timing with different bandwidths, 5, 10, 15, 20, 25, 30
 
 - draw figure of sizing of different time intervals of openface running when capturing pictures
 
 - image layer details
    - aufs-tree-fd, apr 12 - apr20.
    - figure-layer-stack.tex, apr19-apr20.
    - docker-intro.tex
 
 - memory difference transfer, done Apr 5, .
 
 - figure of pre-dump stages, done Apr 9, post in paper, only 5mbps, evaluation part, Apr 11.
 
 - bandwidth control, done Apr 5; desription in paper, Evaluation part, Apr 11.

v4: Mar 29, 2017
    
    - done docker image layer investigation.
    - done image layer ID remapping and restore on it.
    
    - get some initial exp data on migrate Docker containers.
    

v3: Mar 18, 2017
    - brief introduction of Docker image management, AUFS storage
    - brief compression explanations.
    
v2: Mar 16, 2017

    - Phaul tool expriment data: 2 Gigabytes transfer size. 
    - Start docker image layer investigation

v1: Mar 14, 2017
    - migration process brief introduction


\fi
%comments end

\input{main-docbody.tex}